Modeling an Economy with Policy Gradients

### 2019-12-05 paper/paper.tex
Fixed methods section

>>>>

[multiagent -> individual RL agents]
[describe state, $s_s$]
[describe actions, $s_a$, as discretized to more easily track the]
[describe rewards]
[parameterizing the demand curve]
[full transparency of staters]

\subsection{RL Algorithms******}
We worked within the realm of policy gradient methods; we chose this family of algorithms

[exploration strategy is built in?]

with large action spaces.

As framed, our problem contains large — in fact, high dimensional — state spaces. Specifically, the dimension of a given state is $s_s = 2 \cdot (\text{number of firms}) + (\text{number of people})$. Furthermore, while the values in each dimension were integers, they could take on a wide range of values. Therefore, in every policy, we use neural network architectures to convert a given state to a vector, containing log probabilities of taking each action. In empirical testing, if $s_a$ is the number of possible actions, we've seen that the following architecture is a simple framework that still yields convergence in our context:
\begin{itemize}
  \item Input layer with state input, of dimension $s_s$. State values are unnormalized.
  \item Hidden layer with tanh activation, of dimension $\left\lfloor \sqrt{s_s \, s_a} \right\rfloor$
  \item Output layer with tanh activation, followed by log softmax, of dimension $s_a$
\end{itemize}
During training, we generally use a learning rate of $\alpha = 0.01$.

\subsubsection{REINFORCE Policy Gradient******}
